\documentclass{handout}
\usepackage{sourceserifpro}

\SetInstructor{Mx. Malone}
\SetCourseTitle{MATH 117: Trigonometry}
\SetSemester{Fall 2021}
\SetHandoutTitle{Final Exam}


\begin{document}
\maketitle

You have two hours. Please show all your work; if I can't follow your logic, I can't give you partial credit.

Your answers should be exact values; please do not answer with decimals.

You are allowed both sides of one 3x5 index card. 

\begin{enumerate}
  \item (10 pts) Two supplementary angles measure \(x^2 + 63\) degrees and \(2x + 18\) degrees. Find the \textbf{positive} value of \(x.\)

    \vspace{20em}

  \item A right triangle has a hypotenuse measuring 41 meters and one side measuring 40 meters. Let \(\theta\) be the angle formed by the 41-meter side and the 40-meter side.
    \begin{enumerate}
      \item (10 pts) Compute \(\sin \theta\), \(\cos \theta\), and \(\tan \theta.\)
        
        \vspace{10em}

      \item (10 pts) Find \(\sin(2\theta)\) and \(\cos(2\theta).\)

        \vspace{20em}
    \end{enumerate}

  \item (10 pts) A right triangle has an angle of 60 degrees opposite a side of \(14\sqrt3\) meters. Draw this triangle (your drawing need not be to scale); compute the other sides and angles; and label them correctly.

  \vspace{20em}

  \item Suppose that \(\sin \theta = -2/9\) and \(\theta\) lies in the third quadrant.
    \begin{enumerate}
      \item (10 pts) Find \(\cos \theta\). Remember to use the correct sign.

        \vspace{15em}

      \item (10 pts) Find \(\tan \theta\), \(\cot \theta\), \(\sec \theta\), and \(\csc \theta\).
        
        \vspace{15em}
    \end{enumerate}

    \newpage

  \item (10 pts) Consider the tangent curve given by \(f(x) = -7 \tan\left(5x - \dfrac{\pi}{2}\right) + 10.\) Find \textbf{three of}: the amplitude/vertical stretching factor, the period, the phase shift, and the midline equation.

    \vspace{25em}

  \item (10 pts) Find \(\tan\left(\arcsin(-1) + \arccos\left(\dfrac{\sqrt2}2\right)\right).\)

    \newpage
  \item (10 pts) Find \(\sin\left(\dfrac{\pi}{4} + \dfrac{\pi}{3}\right)\) and \(\cos\left(\dfrac{\pi}{3} - \dfrac{\pi}{4}\right).\)

    \vspace{20em}
  \item (10 pts) Find all solutions \(\theta\) between \(0 \leq \theta < 2\pi\) of the equation \(\tan^2 \theta = \tan \theta.\)
\end{enumerate}

\vspace{30em}

It's been a pleasure having you this semester. Best of luck in whatever you may do next. :)

\end{document}
